\documentclass[a4paper,11pt]{extarticle}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks,pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{calc}
\usepackage[top=0.55in, left=0.57in, right=0.57in]{geometry}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\textheight}{11in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]
%-------------------------
% Custom commands
\newcommand{\resumeSkillItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeItem}[1]{
	\item\small{
		#1 \vspace{-1.2pt}
	}
}

\newcommand{\resumeItemWithoutTitle}[1]{
	\item\small{
		{\vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}
    \item
		\begin{tabular*}{1\linewidth}{l@{\extracolsep{\fill}}r}
			\textbf{#1} & #2 \\
			\textit{#3} & \textit{#4} \\
		\end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeSubItem}[2]{\resumeSkillItem{#1}{#2}\vspace{-5pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{
    \begin{itemize}[leftmargin=0.15in,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\vspace{-3pt}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-----------------------------
%%%%%%	CV STARTS HERE	%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{{\LARGE Aditya Diwakar}} 
		& 
    \underline{\href{https://github.com/adityaxdiwakar}
        {github.com/adityaxdiwakar}}\\
	\underline{\href{mailto:aditya.diwakar@gatech.edu}
        {aditya.diwakar@gatech.edu}}
		&(470) 302-9648 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
	\resumeSubHeadingListStart
		\resumeSubheading
			{Georgia Institute of Technology}{Atlanta, GA}
            {Dual B.S. in Computer Science \& Mathematics, 
                GPA: 3.95 / Major GPA: 4.0}
			{Aug 2020 -- Dec 2023}
			\vspace{-3pt}
			{\scriptsize { \footnotesize{\newline{}\textbf{Dual Enrolled:}
                2019 -- 2020 (Part-Time), 2020 -- 2021 (Full-Time)
			}}}
			{\scriptsize { \footnotesize{\newline{}\textbf{Concentrations:}
				Systems \& Architecture, Machine Learning; Probability \& 
				Statistics
			}}}
			{\scriptsize { \footnotesize{\newline{}\textbf{Courses:}
                \textit{Combinatorial Analysis}, \textit{Compilers},
                Processor Design, Operating Systems, Real Analysis,
                Automata Theory, 
                \hspace{\linewidth} \hspace*{41pt}
                Systems \& Networks, Computer Architecture, Machine Learning,
                Stochastic Processes, Numerical Analysis
			}}}
	\resumeSubHeadingListEnd

\section{Experience}
	\resumeSubHeadingListStart
        \resumeSubheading
            {Citadel Securities}
            {Chicago, IL}
            {Incoming Software Engineering Intern}
            {May 2023 -- Aug 2023}
        \resumeSubheading
            {D. E. Shaw \& Co.}
            {New York, NY}
            {Software Engineering Intern}
            {May 2022 -- Aug 2022}
		\resumeItemListStart
            \resumeItem{Reduced cost of automation \& SRE toil by
                designing a framework to easily deploy infrastructure
                workflows.}
            \resumeItem{Implemented GSSAPI SSH handshake to programatically
                interact with Kerberos-secured host machines.}
            \resumeItem{Built dial tone service to ensure reliability during
                outages \& monthly releases by leveraging Temporal.io.}
            \resumeItem{Increased automation workflow visibility by providing
                Elasticsearch integration by default.}
		\resumeItemListEnd
		\resumeSubheading
            {Loganov Data}
            {Remote}
		    {Founder, Software Engineer}
            {Jun 2020 -- Jul 2021}
		\resumeItemListStart
			\resumeItem{Forecasted natural gas demand volatility with 92\%
                accuracy through probabilistic \& regressive models}
			\resumeItem{Ingested weather vendor data 6x faster than industry
				standard through low-level parallel processing}
		\resumeItemListEnd
		\resumeSubheading
            {NetVPX Hosting}
            {Remote}
		    {VP, Software Engineer}
            {Oct 2018 -- Jul 2019}
		\resumeItemListStart
			\resumeItem{Led initiatives to develop custom hosting provisioning
				tools and additional product SKUs.}
			\resumeItem{Ensured $99.97$\% site reliability SLA obligations
                by deploying comprehensive monitoring suite.}
		\resumeItemListEnd
	\resumeSubHeadingListEnd

\section{Academia}
	\resumeSubHeadingListStart
        \resumeSubheading
            {Georgia Institute of Technology}
            {Atlanta, GA}
            {Undergraduate Researcher --- Habanero Extreme Scale Software Lab}
            {Aug 2022 -- Present}
        \resumeSubheading
            {Georgia Institute of Technology}
            {Atlanta, GA}
            {Lead Teaching Assistant}
            {Jan 2022 -- May 2022}
		\resumeItemListStart
			\resumeItem{Taught algorithm design, recurrences, graph
            theory, and complexity theory to 200+ students.}
            \resumeItem{Ensured course and student success by organizing 
                assignments/exams and delegating work for other TAs.}
            \resumeItem{Achieved 4.98/5 student rating through course management,
                grading orchestration, and transparency.}
		\resumeItemListEnd
	\resumeSubHeadingListEnd

\section{Projects}
    \noindent
    \begin{itemize}
        \vspace{-1.5mm}
        \item{\textbf{OCamLC-3:} Developed assembler for LC-3 assembly with
                custom lexing, parsing, and assembling. Created CLI with
                outputs for lexed, parsed, and assembled states. Written
                in OCaml.
        }
        \vspace{-1mm}
        \item{\textbf{Open Exchange:} Implemented exchange in OCaml
                supporting multiple order types; profiled \& optimized data
                structures with \texttt{ocamlprof}. Supported redundant
                matching engines \& cancel fairies.
        }
        \vspace{-1mm}
        \item{\textbf{Flux:} Provided developer friendly Go SDK to communicate
                with TDAmeritrade WebSocket data provider. Built model to
                convert from subscription data model to requester/receiver
                model. 
        }
    \end{itemize}

\section{Skills Summary}
	\resumeSubHeadingListStart
		\resumeSubItem{Languages}
            {\hspace{0.6mm}~~~~~~~C++20, Go, OCaml, Rust, C, Python, x86
                Assembly, RISC-V, Java, Rust, \LaTeX}
		\resumeSubItem{Tools}
            {\hspace{0.3mm}~~~~~~~~~~~~~~~Linux, Docker, SQL, CI/CD, Prometheus,
            Grafana, Multicast Networking}
		\resumeSubItem{Infrastructure}
            {~~Routing/Switching, Distributed Systems, Matching Engines, Low
            Latency Development}
        \resumeSubItem{Interests}
            {~~~~~~~~~~Probability Theory, Travel, Espresso, Personal Finance,
            Gardening}

        \begin{comment}
		\resumeSubItem{Finance}
			{\hspace{0.7mm}~~~~~~~~~~~Futures, Options, Stochastics, Hypothesis
				Testing, Commodities, Volatility}
        \end{comment}


	\resumeSubHeadingListEnd
\end{document}
